\section{Conclusion and Future Work}
\label{section: conclusion}

We proposed \NAME{}, a machine-learning based ensemble method to aggregate various anti-pattern detection approaches on the basis of their internal detection rule. The goal is to create an improved classifier with respect to the standalone approaches. Our method consists in identifying the core-metrics of each approach to be aggregated and then use these metrics to feed a neural-network classifier. To train and evaluate our model, we built an oracle containing the occurrences of God Class and Feature Envy in eight open-source systems. To address the poor performances commonly reported by neural-networks on imbalanced datasets such as our oracle, we also designed a training procedure allowing to maximize the expected MCC. Then, we evaluated \NAME{} on this oracle and compared its performances with the so aggregated tools as well as with competing ensemble methods. Key results of our experiments indicate that:

\begin{itemize}
\item \NAME{} significantly outperforms the standalone tools aggregated through our approach in detecting God Class and Feature Envy and performs well independently of the systems characteristics.

\item \NAME{} outperforms other ensemble methods in terms of recall and MCC. Also, none of the competing ensemble method (i.e., Vote and ASCI) has succeeded to improve the detection for both anti-patterns.
\end{itemize}

Future work includes a comparative study of the different machine-learning algorithms that could be used for aggregation. We also plan to extend our approach to the detection of other anti-patterns with a greater number of detection tools.