%\documentclass[preprint,2p,twocolumn]{elsarticle}
\documentclass[final,2p,times,twocolumn]{elsarticle}
\usepackage[utf8]{inputenc}

\usepackage{natbib}
\usepackage[font=normalsize]{caption}
\usepackage{graphicx}
\usepackage{amsmath, bm, amsfonts}
\usepackage{stmaryrd}
\usepackage{multirow, adjustbox, chngpage}
\usepackage{bigstrut}
\usepackage{fancybox}
\usepackage[flushleft]{threeparttable}
\usepackage{color}
\usepackage{balance}
\usepackage[top=1in, textwidth=19cm]{geometry}
\columnsep=1.6em



\journal{Journal of Systems and Software}

\newcommand\Foutse[1]{\nbc{FK}{#1}{blue}}
\newcommand{\NAME}{SMAD}
\newcommand{\RQone}{Does \NAME{} outperform standalone detection tools?}
\newcommand{\RQtwo}{Does \NAME{} outperform other ensemble methods?}

\DeclareMathOperator*{\maxx}{max}
\DeclareMathOperator*{\argmax}{argmax}
\DeclareMathOperator*{\argmin}{argmin}

\newcommand{\Answer}[1]{\begin{center}%    
    \noindent\thicklines\setlength{\fboxsep}{8pt}%    
    \cornersize{0.2}\Ovalbox{\begin{minipage}{8.5cm}%    
    \textit{#1}\end{minipage}} \end{center}}

\begin{document}
\begin{frontmatter}
\title{A Machine-learning Based Ensemble Method For Anti-patterns Detection}

\author[poly]{Antoine Barbez}
\ead{antoine.barbez@polymtl.ca}

\author[poly]{Foutse Khomh}
\ead{foutse.khomh@polymtl.ca}

\author[concordia]{Yann-Gaël Guéhéneuc}
\ead{yann-gael.gueheneuc@concordia.ca}

\address[poly]{Polytechnique Montreal}
\address[concordia]{Concordia University}

\begin{abstract}
Anti-patterns are poor solutions to recurring design problems. Several empirical studies have highlighted their negative impact on program comprehension, maintainability, as well as fault-proneness. A variety of detection approaches have been proposed to identify their occurrences in source code. However, these approaches can identify only a subset of the occurrences and report large numbers of false positives and misses. Furthermore, a low agreement is generally observed among different approaches. Recent studies have shown the potential of machine-learning models to improve this situation. However, such algorithms require large sets of manually-produced training-data, which often limits their application in practice. 

In this paper, we present SMAD (SMart Aggregation of Anti-patterns Detectors), a machine-learning based ensemble method to aggregate various anti-patterns detection approaches on the basis of their internal detection rules. Thus, our method uses several detection tools to produce an improved prediction from a reasonable number of training examples. We implemented SMAD for the detection of two well known anti-patterns: God Class and Feature Envy. With the results of our experiments conducted on eight java projects, we show that: (1) our method clearly improves the so aggregated tools; (2) SMAD significantly outperforms other ensemble methods.
\end{abstract}

\begin{keyword}
Software Quality, Anti-patterns, Machine Learning, Ensemble Methods
\end{keyword}

\end{frontmatter}

\input{01Introduction}
\input{02RelatedWork}
\input{03SMAD}
\input{04Methodology}
\input{05Study}
\input{06Threats}
\input{07Conclusion}
\section*{Acknowledgement}
This work is partly supported by the The Natural Sciences and Engineering Research Council of Canada (NSERC) and the Canada Research Chair on Patterns in Mixed-language Systems.
\section{References}
\balance
\bibliographystyle{plain}
\bibliography{references}
\end{document}
