\section{Related Work}
To combat crimes in blockchain, transaction tracing is a critical task for blockchain security companies and the community. Current methods for blockchain transaction tracing are mainly designed for Bitcoin-like blockchain systems and heavily rely on expert experience. The most widely used transaction tracing method is Breath First Search (BFS) \cite{zhao2015graph,phetsouvanh2018egret}, and many related tools like skytrace\footnote{https://www.certik.com/skytrace} and coinholmes\footnote{https://trace.coinholmes.com} are available. Since BFS is insufficient to reveal the audit priority of different money tracking directions, the taint analysis technologies \cite{moser2014towards,tironsakkul2019probing,di2015bitconeview} have been proposed for bitcoin tracing according to the amount value and the order of multiple outputs in each transaction. However, these technologies rely on expert analysis and cannot automatically output the money flows from the source to the targets.

Based on the co-spending clustering heuristic in Bitcoin that the input addresses of the same transaction belong to the same entity \cite{Reid2013}, Huang et al. proposed to track the bitcoin flow of ransomware to when the money is being cashed out \cite{HuangTracking2018}.
% Tracking Ransomware End-to-end
Meiklejohn et al. \cite{meiklejohn2013fistful} utilized the change address heuristic to deanonymize the money flows in Bitcoin.
Moreover, some rule-based transaction tracing methods were proposed for cross-chain scenarios and mixing scenarios. For example, Yousaf et al. traced the cross-chain money flows by identifying the transactions which happen close in time and have similar amount value \cite{yousaf2019tracing}. 
However, these rule-based methods are designed for specific protocols and they are inapplicable to transaction tracing in account-based blockchains.

Personalized PageRank models the relevance of nodes in a network to a specific node, and has been widely used in web search \cite{page1999pagerank}, recommendations \cite{WTFGupta2013}, etc. Recently many variants and efficient approximations of personalized PageRank have been proposed for large-scale applications \cite{bojchevski2020scaling}. In this paper, we model the account-based blockchain data as a directed, weighted, temporal, and multi-relationship graph, and formalize the transaction tracing problem as a graph searching problem. We develop a scalable and intelligent transaction tracing tool for account-based blockchains based on personalized PageRank and its approximate solutions.