\documentclass[acmsmall]{acmart}

\usepackage{booktabs}
\usepackage{vcell}
\usepackage{subfloat}
\usepackage{booktabs}
 \usepackage{arydshln}
 
\usepackage{amsmath}
\usepackage[normalem]{ulem}

\newcommand{\rnr}[1]{{\color{black}{#1}}}
\newcommand{\newcscw}[1]{{\color{black}{#1}}}
\newcommand{\mrev}[1]{{\color{black}{#1}}}


\newcommand{\msb}[1]{{\color{blue}{MSB: #1}}}
\newcommand{\joseph}[1]{{\color{purple}{JS: #1}}}
\newcommand{\sahil}[1]{{\color{brown}{SY: #1}}}
\newcommand{\cp}[1]{{\color{green}{CP: #1}}}
\newcommand{\mlg}[1]{{\color{cyan}{MLG: #1}}}
\newcommand{\ch}[1]{{\color{red}{CH: #1}}}


\AtBeginDocument{%
  \providecommand\BibTeX{{%
    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}}


% FOR ARXIV
\setcopyright{acmcopyright}
\copyrightyear{2022}
\acmYear{2022}
\acmDOI{xx.xxxx/xxxxxxx.xxxxxxx}
\acmConference[CSCW '22]{This work will appear in CSCW '22: Proc. ACM Hum.-Comput. Interact}{November 03--05, 2022}{Woodstock, NY}
\acmBooktitle{This work will appear in CSCW '22: Proc. ACM Hum.-Comput. Interact,
  June 03--05, 2022, Woodstock, NY}
\acmPrice{15.00}
\acmISBN{978-1-4503-XXXX-X/18/06}

% FOR REAL
% \setcopyright{acmlicensed}
% \acmJournal{PACMHCI}
% \acmYear{2022} \acmVolume{6} \acmNumber{CSCW2} \acmArticle{451} \acmMonth{11} \acmPrice{15.00}\acmDOI{10.1145/3555552}



\begin{document}

%% The "title" command has an optional parameter,
%% allowing the author to define a "short title" to be used in page headers.
\title[Measuring the Prevalence of Anti-Social Behavior]{Measuring the Prevalence of Anti-Social Behavior in Online Communities}

\author{Joon Sung Park}
\affiliation{%
 \institution{Stanford University}
 \streetaddress{353 Jane Stanford Way}
 \city{Stanford}
 \state{California}
 \country{USA}}
\email{joonspk@stanford.edu}

\author{Joseph Seering}
\affiliation{%
 \institution{Stanford University}
 \streetaddress{353 Jane Stanford Way}
 \city{Stanford}
 \state{California}
 \country{USA}}
\email{seeringj@stanford.edu}

\author{Michael S. Bernstein}
\affiliation{%
 \institution{Stanford University}
 \streetaddress{353 Jane Stanford Way}
 \city{Stanford}
 \state{California}
 \country{USA}}
\email{msb@cs.stanford.edu}

\renewcommand{\shortauthors}{Joon Sung Park et al.}

\begin{abstract}
    With increasing attention to online anti-social behaviors such as personal attacks and bigotry, it is critical to have an accurate accounting of how widespread anti-social behaviors are. In this paper, we empirically measure the prevalence of anti-social behavior in one of the world's most popular online community platforms. We operationalize this goal as measuring the proportion of unmoderated comments in the 97 most popular communities on Reddit that violate eight widely accepted platform norms. To achieve this goal, we contribute a human-AI pipeline for identifying these violations and a bootstrap sampling method to quantify measurement uncertainty. We find that 6.25\% (95\% Confidence Interval [5.36\%, 7.13\%]) of all comments in 2016, and 4.28\% (95\% CI [2.50\%, 6.26\%]) in 2020-2021, are violations of these norms. Most anti-social behaviors remain unmoderated: moderators only removed one in twenty violating comments in 2016, and one in ten violating comments in 2020. Personal attacks were the most prevalent category of norm violation; pornography and bigotry were the most likely to be moderated, while politically inflammatory comments and misogyny/vulgarity were the least likely to be moderated. This paper offers a method and set of empirical results for tracking these phenomena as both the social practices (e.g., moderation) and technical practices (e.g., design) evolve.


\end{abstract}

%%
%% The code below is generated by the tool at http://dl.acm.org/ccs.cfm.
%% Please copy and paste the code instead of the example below.
%%
\begin{CCSXML}
<ccs2012>
   <concept>
       <concept_id>10003120.10003130.10011762</concept_id>
       <concept_desc>Human-centered computing~Empirical studies in collaborative and social computing</concept_desc>
       <concept_significance>500</concept_significance>
       </concept>
 </ccs2012>
\end{CCSXML}

\ccsdesc[500]{Human-centered computing~Empirical studies in collaborative and social computing}

%% Keywords. The author(s) should pick words that accurately describe
%% the work being presented. Separate the keywords with commas.
\keywords{moderation, anti-social behavior, online communities}


\maketitle

% content is what we had prior to the 2022 Jan 15 submission
% content_RnR_redmarked is from the 2022 Jan 15 submission
% content_minor_revision__Apr2022 is for the 2022 Apr minor revision submission

\input{content_minor_revision__Apr2022/introduction}
\input{content_minor_revision__Apr2022/related_work}
\input{content_minor_revision__Apr2022/method}
\input{content_minor_revision__Apr2022/method-pt2}
\input{content_minor_revision__Apr2022/method-pt3}
\input{content_minor_revision__Apr2022/results}
\input{content_minor_revision__Apr2022/discussion}
\input{content_minor_revision__Apr2022/conclusion}


%% The next two lines define the bibliography style to be used, and
%% the bibliography file.
\bibliographystyle{ACM-Reference-Format}
\bibliography{main}

\appendix
\input{content_minor_revision__Apr2022/appendix}


\end{document}
\endinput