%!TEX root = ./binder.tex
%-------------------------------------------------------------------------------
%-------------------------------------------------------------------------------

\begin{abstract} 
Code coverage analysis plays an important role in the software testing process. 
More recently, the remarkable effectiveness of coverage feedback has triggered a broad interest in feedback-guided fuzzing.
In this work, we introduce {\bcov}, a tool for binary-level coverage analysis.
Our tool statically instruments x86-64 binaries in the ELF format without compiler support.
We implement several techniques to improve efficiency and scale to large real-world software.
First, we bring Agrawal's probe pruning technique to binary-level instrumentation and effectively leverage its superblocks to reduce overhead.
Second, we introduce \textit{sliced microexecution}, a robust technique for jump table analysis which improves CFG precision and enables us to instrument jump table entries.
Additionally, smaller instructions in \mbox{x86-64} pose a challenge for inserting detours.
To address this challenge, we aggressively exploit padding bytes and systematically host detours in neighboring basic blocks.

We evaluate {\bcov} on a corpus of 95 binaries compiled from eight popular and well-tested packages like FFmpeg and LLVM.
Two instrumentation policies, with different edge-level precision, are used to patch all functions in this corpus - over 1.6 million functions.
Our precise policy has average performance and memory overheads of 14\% and 22\% respectively.
Instrumented binaries do not introduce any test regressions.
The reported coverage is highly accurate with an average F-score of 99.86\%.
Finally, our jump table analysis is comparable to that of \textsf{IDA Pro} on \textsf{gcc} binaries and outperforms it on \textsf{clang} binaries.

\end{abstract}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
