%!TEX root = ./binder.tex
%-------------------------------------------------------------------------------
\section{Conclusion}
%-------------------------------------------------------------------------------

In this work, we presented {\bcov}, a tool for binary-level coverage analysis.
We implement a trampoline-based instrumentation approach and demonstrate that it can be both efficient and transparent while scaling to large C/C++ programs.
However, this required an orchestrated effort where we leverage probe pruning, improve CFG precision, and cope with the instruction-size variability in x86-64 ISA.
Our tool statically instruments ELF binaries without compiler support. 
It largely avoids the need to modify the build system and, consequently, allows for high usability.
Also, we show that the produced coverage report is highly accurate, which can offer a valuable addition to the testing workflow.
We make our tool and dataset publicly available to foster further research in this area.

%%-------------------------------------------------------------------------------
\section*{Acknowledgments}
%%-------------------------------------------------------------------------------
We would like to thank the anonymous reviewers of  ESEC/FSE and USENIX Security for their insightful comments. 
Also, we would like to thank Fangrui Song for the helpful feedback.
Deeban Babu provided assistance with BAP and \texttt{angr} experiments. 
This research has been funded by the federal state of Rhineland-Palatinate, Germany.

\balance


%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
