%
% File emnlp2020.tex
%
%% Based on the style files for ACL 2020, which were
%% Based on the style files for ACL 2018, NAACL 2018/19, which were
%% Based on the style files for ACL-2015, with some improvements
%%  taken from the NAACL-2016 style
%% Based on the style files for ACL-2014, which were, in turn,
%% based on ACL-2013, ACL-2012, ACL-2011, ACL-2010, ACL-IJCNLP-2009,
%% EACL-2009, IJCNLP-2008...
%% Based on the style files for EACL 2006 by 
%%e.agirre@ehu.es or Sergi.Balari@uab.es
%% and that of ACL 08 by Joakim Nivre and Noah Smith

\documentclass[11pt,a4paper]{article}
\usepackage[hyperref]{emnlp2020}
\usepackage{times}
\usepackage{latexsym}
\usepackage{xcolor}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{tipa}
\usepackage{float}
\usepackage{amssymb,amsmath,amsthm,enumitem}
\usepackage{subcaption}
\usepackage{fdsymbol}
\renewcommand{\UrlFont}{\ttfamily\small}

\usepackage{bm}


% This is not strictly necessary, and may be commented out,
% but it will improve the layout of the manuscript,
% and will typically save some space.
\usepackage{microtype}

\aclfinalcopy % Uncomment this line for the final submission
\def\aclpaperid{2493} %  Enter the acl Paper ID here


\DeclareMathOperator{\dec}{dec}
\DeclareMathOperator{\deca}{dec^1}
\DeclareMathOperator{\decb}{dec^2}
\DeclareMathOperator{\enca}{enc^1}
\DeclareMathOperator{\encb}{enc^2}
\DeclareMathOperator*{\softmax}{softmax}

\newcommand{\ascal}{\alpha}

\newcommand{\xvec}{\mathbf{x}}
\newcommand{\tvec}{\mathbf{t}}
\newcommand{\avec}{\mathbf{\alpha}}
\newcommand{\fvec}{\mathbf{f}}
\newcommand{\hvec}{\mathbf{h}}
\newcommand{\vvec}{\mathbf{v}}
\newcommand{\cvec}{\mathbf{c}}
\newcommand{\svec}{\mathbf{s}}
\newcommand{\yvec}{\mathbf{y}}
\newcommand{\step}[1]{_{#1}}
\newcommand{\fst}{^1}
\newcommand{\snd}{^2}

\usepackage{rotating}
\usepackage{multirow}

\usepackage{tikz}
\usetikzlibrary{shapes.geometric}
\usetikzlibrary{patterns}
\usepackage{pgfplots}
\pgfplotsset{compat=1.15}


%\setlength\titlebox{5cm}
% You can expand the titlebox if you need extra space
% to show all the authors. Please do not make the titlebox
% smaller than 5cm (the original size); we will check this
% in the camera-ready version and ask you to change it back.

\newcommand\BibTeX{B\textsc{ib}\TeX}

\renewcommand{\sectionautorefname}{Section}
\renewcommand{\subsectionautorefname}{Section}

\DeclareMathOperator*{\argmax}{arg\,max}
\renewcommand{\arraystretch}{1.2}

\newcommand{\ba}{`}

\newcommand\blfootnote[1]{%
  \begingroup
  \renewcommand\thefootnote{}\footnote{\noindent #1}%
  \addtocounter{footnote}{-1}%
  \endgroup
}

\definecolor{burntred}{HTML}{E66101}
\definecolor{burntblue}{HTML}{00A2FF}


\title{OCR Post Correction for Endangered Language Texts}

\author{Shruti Rijhwani,\textsuperscript{$1$} Antonios Anastasopoulos,\textsuperscript{$2,\dagger$} Graham Neubig\textsuperscript{$1$}  \\
  \textsuperscript{$1$}Language Technologies Institute, Carnegie Mellon University\\
  \textsuperscript{$2$}Department of Computer Science, George Mason University\\
  \texttt{\{srijhwan,gneubig\}@cs.cmu.edu},\quad\texttt{antonis@gmu.edu}}

\date{}

\begin{document}

\maketitle
\begin{abstract}
There is little to no data available to build natural language processing models for most endangered languages. However, textual data in these languages often exists in formats that are not machine-readable, such as paper books and scanned images. In this work, we address the task of extracting text from these resources. We create a benchmark dataset of transcriptions for scanned books in three critically endangered languages and present a systematic analysis of how general-purpose OCR tools are not robust to the data-scarce setting of endangered languages. We develop an OCR post-correction method tailored to ease training in this data-scarce setting, reducing the recognition error rate by 34\% on average across the three languages.\blfootnote{$\dagger$: Work done at Carnegie Mellon University.}\footnote{Code and data are available at \url{https://shrutirij.github.io/ocr-el/}.}
\end{abstract}

\input{sections/1.introduction}
\input{sections/2.problem_setting}
\input{sections/3.dataset}
\input{sections/4.ocr_analysis}
\input{sections/5.model}
\input{sections/6.experiments}
\input{sections/7.related_work}
\input{sections/8.conclusion}

\section*{Acknowledgements}
We thank David Chiang, Walter Scheirer, and William Theisen for initial discussions on the project, the University of Notre Dame Library for the scanned ``Kutune Shirka" Ainu-Japanese book, and Josep Quer for the scanned Griko folk-tales book. We also thank Taylor Berg-Kirkpatrick, Shuyan Zhou, Zi-Yi Dou, Yansen Wang, Zhen Fan, and Deepak Gopinath for feedback on the paper.

This material is based upon work supported in part by the National Science Foundation under Grant No. 1761548. Shruti Rijhwani is supported by a Bloomberg Data Science Ph.D. Fellowship.


\bibliographystyle{acl_natbib}
\bibliography{emnlp2020}

\newpage
\input{sections/appendix}


\end{document}
