%%%%%%%%%%%%%%%%%%%%%%acronym.tex%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% sample list of acronyms
%
% Use this file as a template for your own input.
%
%%%%%%%%%%%%%%%%%%%%%%%% Springer Nature%%%%%%%%%%%%%%%%%%%%%%%%%%

\extrachap{Acronyms}

%Lists of abbreviations\index{acronyms, list of}, symbols\index{symbols, list of} and the like are easily formatted with the help of the Springer Nature enhanced \verb|description|\quad~environment.

\begin{description}%[CABR]

\item[A]~\\
\verb|ACM|\quad~Association for Computing and Machinery -- See \url{www.acm.org}

\verb|API|\quad~Application Programming Interface

\verb|AI|\quad~Artificial Intelligence

\verb|AST|\quad~Abstract Syntax Tree

\verb|AUG|\quad~API Update Graph -- See \chap{SLU}.

\verb|AWS|\quad~Amazon Web Services -- A cloud computing platform proposed by Amazon. See \url{aws.amazon.com}

\item[B]~\\
\verb|BPMN|\quad~Business Process Modeling Notation


\item[C]~\\
\verb|CE|\quad~Collateral Evolution -- See \chap{COL}.

\verb|CHAOSS|\quad~Community Health Analytics in Open Source Software -- See \url{chaoss.community}

\verb|CI|\quad~Continuous Integration -- See \verb|CI/CD|.

\verb|CI/CD|\quad~Continuous Integration, Deployment and Delivery

\verb|CNN|\quad~Convolutional Neural Network -- A specific kind of Neural Network. %(\verb|NN|). 

\verb|CPS|\quad~Cyber-Physical System

\verb|CSP|\quad~Constraint Satisfaction Problem

\verb|CSV|\quad~Comma Separated Values -- A very simple data format.


\item[D]~\\
\verb|DAO|\quad~Data Access Object

\verb|DAG|\quad~Directed Acyclic Graph

\verb|DB|\quad~Database

\verb|DBMS|\quad~Database Management System

\verb|DE&I|\quad~Diversity, Equity and Inclusion -- A set of principles to build inclusive and welcoming workspaces and environments for less privileged individuals or organisations.

\verb|DL|\quad~Deep Learning -- A branch of Artificial Intelligence %(\verb|AI|)
 focused on developing algorithms and applications based on Neural Networks. %(\verb|NN|). 

\verb|DSL|\quad~Domain-Specific Language

\verb|DT|\quad~Decision Tree -- A specific kind of \emph{supervised} machine learning %(\verb|ML|) 
where the classifier is modeled as a tree.


\item[E]~\\
\verb|EIC|\quad~Error-Inducing Change

\verb|EMF|\quad~Eclipse Modeling Framework

\verb|EMR|\quad~Electronic Medical Record

\verb|EOSC|\quad~European Open Science Cloud -- a European Commission initiative aiming at developing an infrastructure providing its users with services promoting open science practices. See \url{eosc-portal.eu}


\item[F]~\\
\verb|FAIR|\quad~Findable, Accessible, Interoperable, Reusable -- Four guiding principles for scientific data management.

\verb|FFNN|\quad~Feed-Forward Neural Network -- A specific kind of Neural Network.% (\verb|NN|). 

\verb|FK|\quad~Foreign Key -- A kind of constraint that is frequently used in relational databases.

\verb|FL|\quad~Federated Learning -- A decentralised form of machine learning %(\verb|ML|)
that can be used to train models on decentralised data.

\verb|FOSS|\quad~Free Open Source Software -- See \verb|OSS|.

\verb|FP|\quad~False Positive

\verb|FSF|\quad~Free Software Foundation -- See \url{www.fsf.org}

\verb|FUSE|~\quad~Filesystem in User SpacE -- See \chap{SWH}.


\item[G]~\\
\verb|GDBT|\quad~Gradient Boosted Decision Tree -- A specific kind of Decision Tree. %(\verb|DT|).

\verb|GDPR|\quad~General Data Protection Regulation -- A data protection law imposed by the European Union.

\verb|GK|\quad~Graph Kernel -- A method to compute the internal weights of a graph neural network. See \chap{MDE}.

\verb|GNN|\quad~Graph Neural Network -- A specific kind of Neural Network. %(\verb|NN|). 

\verb|GNU|\quad~Recurvise acronym for GNU's Not Unix

\verb|GraphQL|\quad~Graph Query Language -- A query language for building flexible, efficient and powerful \verb|API|s.

\item[H]~\\
\verb|HQL|\quad~Hibernate Query Language -- An \verb|SQL|-like query language for Hibernate.


\item[I]~\\
\verb|IaC|\quad~Infrastructure as Code

\verb|ICSME|\quad~International Conference on Software Maintenance and Evolution -- The name of an annual scientific \verb|IEEE| conference.

\verb|IDE|\quad~Integrated Development Environment

\verb|IEEE|\quad~Institute of Electrical and Electronics Engineers -- See \url{www.ieee.org}

\verb|INRIA|\quad~Institut National de Recherche en Informatique et en Automatique -- French National Institute for Research in Computer Science and Control

\verb|IT|\quad~Information Technology


\item[J]~\\
\verb|JDBC|\quad~Java Database Connectivity

\verb|JDK|\quad~Java Development Kit

\verb|JPA|\quad~Jakarta Persistence API (formerly known as Java Persistence API) -- A Java specification to manage object-relational mappings (\verb|ORM|) between Java applications and a relational database.

\verb|JSON|\quad~JavaScript Object Notation -- A human-readable data serialisation language and file format, just like \verb|XML| and \verb|YAML|.


\item[L]~\\
\verb|LOC|\quad~Lines of Code

\verb|LR|\quad~Linear Regression

\verb|LSTM|\quad~Long Short-Term Memory -- A specific kind of Recurrent Neural Network. %(\verb|RNN|). 


\item[M]~\\
%\verb|MDD|\quad~Model-Driven Development -- See \verb|MDE|

\verb|MDE|\quad~Model-Driven (Software) Engineering

\verb|ML|\quad~Machine Learning -- A branch of computer science that uses algorithms trained on data to produce models that can perform complex tasks such as analysing, reasoning and learning.

\verb|MOF|\quad~Meta-Object Facility -- A domain-specific modeling language proposed by the \verb|OMG| for specifying metamodels for a variety of modeling languages (including \verb|UML|) to be used in the context of \emph{software engineering} (\ie for specifying, analysing, designing, verifying and validating software systems).

\verb|MSR|\quad~Mining Software Repositories -- The name of an annual scientific \verb|IEEE| conference.


\item[N]~\\
\verb|NATO|\quad~North Atlantic Treaty Organization -- See \url{www.nato.int}

\verb|NB|\quad~Na\"ive Bayesian -- A specific kind of \emph{supervised} machine learning %(\verb|ML|) 
technique.

\verb|NIST|\quad~National Institute of Standards and Technology -- Part of the US Department of Commerce. See \url{www.nist.gov}

\verb|NLP|\quad~Natural Language Processing -- A branch on the intersection of computer science and computational linguistics focused understanding, interpreting and manipultating \emph{natural} (\ie \emph{human}) language.

\verb|NN|\quad~Neural Network -- A computational technique in the area of Artificial Intelligence (\verb|AI|) that is at the heart of Deep Learning (\verb|DL|) algorithms.

\verb|NoSQL|\quad~Not Only SQL or non-SQL -- An category of database management systems %(\verb|DBMS|)
 that enable storing and querying data outside the traditional relational \verb|DBMS| that rely on \verb|SQL| as a query language.

\verb|NVD|\quad~National Vulnerability Database -- A software security vulnerability database maintained by \verb|NIST|. See \url{nvd.nist.gov}

\item[O]~\\
\verb|OCI|\quad~Oracle Cloud Infrastructure

\verb|OCL|\quad~Object Constraint Language -- A query and constraint language proposed by the \verb|OMG| to be used to query or express constraints over models (\eg \verb|UML| and \verb|SysML|) or metamodels (\eg \verb|MOF|).

\verb|OMG|\quad~Object Management Group -- An international non-profit consortium focused on developing technology standards such as \verb|UML|, \verb|SysML| and many more.

\verb|ORM|\quad~Object Relational Mapping -- A technique or framework used to simplify the mapping and translation between object-oriented programs and relational databases.

\verb|OS|\quad~Operating System

\verb|OSI|\quad~Open Source Initiative -- See \url{opensource.org}

\verb|OSS|\quad~Open Source Software


\item[P]~\\
\verb|PDG|\quad~Program Dependency Graph

\verb|PNG|\quad~Portable Network Graphic -- A data format for image files.

\verb|PR|\quad~Pull Request


\item[Q]~\\
\verb|QA|\quad~Quality Assurance

\verb|Q&A|\quad~Question and Answer


\item[R]~\\
\verb|RAM|\quad~Random Access Memory

\verb|REST|\quad~Representational State Transfer -- An architectural style for allowing computer systems to communicate with each other.

\verb|RF|\quad~Random Forest -- A specific kind of  supervised machine learning %(\verb|ML|)
technique.

\verb|RL|\quad~Reinforcement Learning -- One of the three machine learning paradigms, alongside \emph{supervised} and \emph{unsupervised} learning.

\verb|RNN|\quad~Recurrent Neural Network -- A specific kind of Neural Network. %(\verb|NN|). 

\verb|ROS|\quad~Robot Operating System -- See \url{www.ros.org}

\verb|RTM|\quad~Relational Topic Model


\item[S]~\\
\verb|SATD|\quad~Self-Admitted Technical Debt -- A specific kind of Technical Debt. %(\verb|TD|).

\verb|SBSE|\quad~Search-Based Software Engineering

\verb|SE|\quad~Software Engineering

\verb|SemVer|\quad~Semantic Versioning -- See \url{semver.org}

\verb|SHA1|\quad~Secure Hash Algorithm 1 -- A well-known cryptographic hash algorithm.

\verb|SPDX|\quad~Software Package Data Exchange -- An open standard for software bill of materials

\verb|SQL|\quad~Structured Query Language -- A language used to query data stored in a relational database.

\verb|SSD|\quad~Social Semantic Diversity

\verb|SVG|\quad~Scalable Vector Graphic -- A data format for image files.

\verb|SVM|\quad~Support Vector Machines -- A specific kind of \emph{supervised} machine learning %(\verb|ML|)
technique.

\verb|SWH|~\quad~Software Heritage -- See \chap{SWH}

\verb|SWHID|~\quad~Software Heritage Persistent Identifier -- See \chap{SWH}

\verb|SysML|\quad~Systems Modeling Language -- A modeling language proposed by the \verb|OMG| to be used in the context of \emph{systems engineering} (\ie specifying, analysing, designing, verifying and validating systems).


\item[T]~\\
\verb|TD|\quad~Technical Debt

\verb|TP|\quad~True Positive


\item[U]~\\
\verb|UML|\quad~Unified Modeling Language -- A modeling language proposed by the \verb|OMG| to be used in the context of \emph{software engineering} (\ie specifying, analysing, designing, verifying and validating software systems).

\verb|UNESCO|\quad~United Nations Educational, Scientific and Cultural Organization -- See \url{www.unesco.org}

\verb|URI|\quad~Uniform Resource Identifier

\verb|URL|\quad~Uniform Resource Locator


\item[V]~\\
\verb|VCS|\quad~Version Control System

\item[X]~\\
\verb|XML|\quad~eXtensible Markup Language -- A human-readable data serialisation language and file format, just like \verb|YAML| and \verb|JSON|.

\verb|XP|\quad~eXtreme Programming -- One of the many agile software development methodologies.


\item[Y]~\\
\verb|YAML|\quad~Recursive acronym for YAML Ain't Markup Language -- A human-readable data serialisation language and file format, just like \verb|XML| and \verb|JSON|.

\end{description}
